---
title: "rfishdraw: Procedurally Generated Fish Drawings Via Javascript"
author: "Liuyong Ding\\

        Institute of International Rivers and Eco-security, Yunnan University"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: false
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{rfishdraw introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteDepends{patchwork}
  %\VignetteDepends{ggplot2}
---

## Introduction

This **rfishdraw** package procedurally generated fish drawings via [ggplot2](https://github.com/tidyverse/ggplot2) based on [fishdraw Javascript](https://github.com/LingDong-/fishdraw) library. 

**Note**: You need to install [nodejs](https://nodejs.org/en/) before using the [rfishdraw](https://github.com/Otoliths/rfishdraw) package.


## Installation

### Windows

Installing nodejs under windows from [nodejs](https://nodejs.org/en/). 

### MacOS

brew search node \\
brew install node@14 \\
brew link node@14 \\
node --version


### Ubuntu

sudo apt-get install nodejs


## Example

##### Load the **rfishdraw** package

```{r}
library("rfishdraw")
library("patchwork")
library("ggplot2")
```

##### Create and implement a custom JS library

```{r }
custom_params(path = "./fishdraw.js",
  save = getwd(),
  body_curve_type = 0,
  body_curve_amount = 0.85,
  body_length = 420,
  body_height = 90,
  scale_type = 1,
  scale_scale = 1,
  pattern_type = 3,
  pattern_scale = 1,
  dorsal_texture_type = 1,
  dorsal_type = 0,
  dorsal_length = 100,
  dorsal_start = 8,
  dorsal_end = 27,
  wing_texture_type = 0,
  wing_type = 0,
  wing_start = 6,
  wing_end = 6,
  wing_y = 0.7,
  wing_length = 130,
  wing_width = 10,
  pelvic_start = 9,
  pelvic_end = 14,
  pelvic_length = 85,
  pelvic_type = 0,
  pelvic_texture_type = 0,
  anal_start = 19,
  anal_end = 29,
  anal_length = 50,
  anal_type = 0,
  anal_texture_type = 0,
  tail_type = 0,
  tail_length = 75,
  finlet_type = 0,
  neck_type = 0,
  nose_height = 0,
  mouth_size = 8,
  head_length = 30,
  head_texture_amount = 60,
  has_moustache = 1,
  moustache_length = 10,
  has_beard = 0,
  has_teeth = 1,
  teeth_length = 8,
  teeth_space = 3.5,
  beard_length = 30,
  eye_type = 0,
  eye_size = 10,
  jaw_size = 1,
  jaw_open = 1)
```


##### Get outputs polylines in svg

```{r }
get_polylines(path = "inst/fishdraw.js",
              format = "smil",
              output = "animated.svg",
              draw_type = "random")
```


##### fish drawings via plot

```{r fig.keep="last"}
file <- system.file("extdata",package = "rfishdraw")
dat <- readRDS(paste0(file,"/","output_json.rds"))
for (i in seq(length(dat))) {
dat[[i]] <- cbind(dat[[i]],i)
}
plot(NA, xlim = c(0,520),ylim = c(-320,0),axes = F,xlab = " ",ylab = " ")
for(i in seq(length(dat))) {
  lines(x = dat[[i]][,1],y = -dat[[i]][,2], lwd=2, col = "blue")
}
```


##### fish drawings via ggplot2

```{r}
fish_draw()

```


##### fish drawings via ggplot2

```{r }

p1 <- fish_draw() +
  theme_void()

p1+p1+p1+p1+p1+p1+plot_layout(ncol = 2)

```



## Contribution

Contributions to this package are welcome. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [**an issue**](https://github.com/Otoliths/rfishdraw/issues).
